openarchaeoCollaboration

### 2023-06-14 analysis/99-conclusion.qmd
temporary commit before pull

Collaborative open source software development in archaeology has seen a rapid and sustained increase beginning around 2014 or 2015. This is marked by a variety of applications and use cases. While there is an emerging community of practice around open source in archaeology, collaboration remains limited. Most work is performed solo and is short-lived.^[**NOTE:** I wonder if we can say something about change over time, for instance, if things are getting better.]

@@

>>>>

Collaborative open source software development in archaeology has seen a rapid and sustained increase beginning around 2014 or 2015. This is marked by a variety of applications and use cases. While there is an emerging community of practice around open source in archaeology, collaboration remains limited. Most work is performed solo and is short-lived.

**NOTE:** I wonder if we can say something about change over time, for instance, if things are getting better.

@@

future work might include qualitative analysis of issues and comments
break out and form new kinds of collaborative commitments suited to this kind of work and the media through with it is performed
relate precarity of central actors with similar phenomena in open source in general
open source is not a magic bullet, it is people, people who are based in the "real world"
